New Insights on the Role of Context in the Perception of a Human-like Robot

### 2015-03-17 main.tex
{ICA->initial tendency to anthropomorphize} + rewrite description of questionaires

@@

Anthropomorphism is seen as a special kind of social (human-like) engagement
with robots. We made an attempt to analyze anthropomorphism in a
\textit{human-robot} interaction by utilizing the gaze patterns of the
participants (who watched this interaction). These gaze patterns were compared
to the gaze patterns for a similar \textit{human-human} interaction setting. The
``human'' part of the human-robot and human-human interactions mentioned above
is only in the form of an audio command and not physically present in the scene.
Hence, we represent the interactions with $\mathcal{R}$ and $\mathcal{H}$ in
this report for the human-robot and human-human settings respectively.

There were four hypotheses made in this experiment. We hypothesized
(\textbf{H1}) that the gaze patterns can distinguish between $\mathcal{H}$ and
$\mathcal{R}$ interaction scenarios. Further, this gaze pattern difference can
be denoted as the distribution of gaze on areas of interest in the scene.
Secondly, we hypothesized (\textbf{H2}) that the difference in gaze patterns
between $\mathcal{H}$ and $\mathcal{R}$ conditions
($\delta_{\mathcal{H},\mathcal{R}}$) correlate with the participants'
\textit{initial capital of anthropomorphism} (ICA), where the ICA was measured
as the sum of the ratings (responses) given by the participants to the questions
of the pre-questionnaire. This means that for participants whose ICA is low, the
gaze patterns should be significantly different for the $\mathcal{R}$ as
compared to that for the $\mathcal{H}$ videos and vice-versa.

We also hypothesized (\textbf{H3}) that the gaze patterns can distinguish
between high-cognitive and low-cognitive tasks. Finally, we hypothesized
(\textbf{H4}) that the cognitive priming will have an effect on the difference
between ICA and \textit{adaptive anthropomorphic perception} (AAP) \ie
$\Delta_{ICA,AAP}$ (where AAP is measured for the post-questionnaire in a
similar way as the ICA).

We used stationary eye tracking technique for tracking the gaze patterns and
``Nao", a robot manufactured by Aldebaran Robotics was used in this
experiment. We prepared the scripts for the robot using Choreographe. The
interactions were recorded as videos and were then shown to the participants.
The scenarios that were covered in the videos were aimed at eliciting the
human-like or high-cognitive (HC) feelings for the robot in one setting and
robot-like or low-cognitive (LC) feelings in the other setting. For example, we
had a scene, where the robot is asked by the human to \textit{``pick up the
brown toy"} and in another scene, with the same video, the robot is asked to
\textit{``pick up its favorite toy"}. We tried to keep our distribution of
participants uniform across all variations of the scenarios to avoid any biases
to our results. The change in the feelings of participants were recorded in the
form of response to two questionnaires before and after the experiment. The
difference in the response of the two questionnaires was used to measure the
impact the videos had on the participants.

As mentioned earlier, the human element in the $\mathcal{R}$ interaction was in
the form of only a human voice, basically a command given by the human to the
robot. This command (\eg ``pick up the brown toy") was used to prime
the context thereby classifying the scenario as LC or HC. Initially we had three
different scenarios where the robot/human was asked:

@@

Differing from first two scenarios, the third scenario had only one object in
the video \ie~the actor (human or robot). In the first two scenarios, a
participant could make gaze transitions, say, between the robot and the toys for
the first scene. In contrast, in the third scene, a participant could only look
at the robot showing its movements. The third scene, hence, was more related to
observing the various body movements and was not helpful in identifying
differences in gaze patterns based on LC and HC scenarios and therefore, we did
not consider it for our study. First, a pilot experiment was conducted with a
small number of participants and then a full-fledged experiment was carried out.

\section{Related Work}

In a human-robot interaction, studying anthropomorphism would essentially mean
the assessment of human's tendency to engage in a human like way with robots
(that are not deliberately made to buttress such relationship). In broader
terms, anthropomorphism can be understood as the phenomenon between a human and
a non-human, where the human tends to attribute human characteristics to the
non-human in order to establish a meaningful contact\cite{fink2014dynamics}. But
there have been a plethora of definitions of anthropomorphism not only across
but within disciplines\cite{duffy_anthropomorphism_2002}. Even
within HRI (human robot interaction) and robotics, there has not been a single
unique definition of anthropomorphism, but a variety of them.
Bartneck~\etal\cite{bartneck_measurement_2008} refer to it as \emph{``the
attribution of a human form, human characteristics, or human behavior to
nonhuman things such as robots, computers, and animals."} Contrarily,
Waytz~\etal\cite{Waytz2010} apply a more psychological-cognitive view and
define anthropomorphism as \textit{``a process of inductive inference whereby
    people imbue the real or imagined behavior of other agents with human like
    characteristics, motivations, intentions, or underlying mental states".}

@@

This study is build as an eye-tracking experiment (mainly measuring fixation times on
various body parts) where participants watch short videos of an agent (either a
robot or a human) performing a very simple task (like picking an object), in
two different \emph{socio-cognitive contexts}. These contexts, created by priming
and/or audio cues, are designed to elicit either a shallow cognitive context
(that participant would refer as a \emph{machine-like} situation) or a deeper
cognitive context (refered as a \emph{human-like} situation).

@@

    \caption{\small The study follows a 2x2 design: the \emph{robot} vs
        \emph{human} condition is within subject, while the \emph{shallow
        cognitive context} vs \emph{deep cognitive context} is between subject.
        Two stimuli (\emph{``toys''} scene, {\bf A}, and \emph{``noise''} scene,
        {\bf B}) were shown to the participants, introduced by brief verbal
        commands, reproduced in the table. While visually identical (see
        screenshots on figure~\ref{fig:stimuli}), the stimuli were introduced
        with different commands in the two conditions \emph{shallow} and
        \emph{deep cognitive
        context}.}

@@

\subsubsection{Dependent Variables}

We have a dependent variable that is the difference between the ICA and AAP.
This represents how much a participant has been affected by watching the videos
because it reflects the difference in the response of a participant in the pre
and post questionnaires.

@@

\section{Course of the study}

@@

The participants were recruited amongst students of our university. To avoid students
with a higher familiarity with robots and artificial intelligent systems,
Computer Science and Electronics curriculum were excluded. This was \textit{a
posteriori} comforted as per the questionnaire responses: no
participants\fxwarning{to be checked}
reported itself as being familiar with robots and only a few\fxwarning{how
many?} out of 40 had ever owned a robot.

@@

\subsubsection{Consent Form}

Before the experiment, participants were made to read, understand and sign a
standard consent form.

\subsubsection{Initial Interaction}

After the pre questionnaire, we kept a 2 to 3 minutes session for initial
interaction, where we let the participant spend some time with Nao.
The purpose of this interaction was to familiarize the participants with the
robot and mitigate the novelty effect, so that they do not get surprised seeing
a robot for the first time in the videos.

\subsubsection{Pre-questionnaire}

Participants were asked to fill the 49 questions questionnaire right after the
initial interaction.

@@

After filling the pre-questionnaire, participants watched the $\mathcal{R}$ and
$\mathcal{H}$ interaction videos.

@@

After watching the videos, participants were asked to fill the post
questionnaire, which was the last step in the procedure of this study.

\subsubsection{Reward}

Each of the participants were given a reward equivalent to CHF 10.

@@

\subsubsection{Questionnaires}

\paragraph{Pre-questionnaire}

The participants were asked to fill a questionnaire which had 49 questions. The
responses to the questions were scaled in the 5-point likert scale, numerically
ranging from -2 to 2. The questionnaire had ten questions from the 10 item
big-five personality questionnaire. And then there were questions taken from
godspeed questionnaire and other questionnaires. Please refer to the appendix
for a sample questionnaire used in this study. The ICA was calculated as the sum
of the ratings/points provided by the participants for questions 30 to 39 as
these were the questions most closely resembling anthropomorphism. In this
report, we refer to this questionnaire as the pre-questionnaire \ie before the
experiment, and it typically took 5 minutes for participants to fill it.

\paragraph{Post-questionnaire}

There was another questionnaire form that was almost identical to the
pre-questionnaire that the participants had to fill after watching the videos.
This questionnaire typically took 3 to 4 minutes to fill and we refer to this as
the post-questionnaire. A sample is provided in the appendix of this report.
Based on the responses filled in this questionnaire, the AAP was calculated as
the sum of the ratings/points provided by the participants for questions 17 to
26 (similar to ICA).

@@

Based on the experiments conducted on 40 participants in the $\mathcal{H}$ and
$\mathcal{R}$ interactions across LC and HC conditions, we have the following
results. (The detailed statistics and code used for obtaining the results are
available here : \url{https://github.com/chili-epfl/anthropomorphism-eyetracking})

@@

Among the 10 AOIs, we grouped the AOIs corresponding to the actor into 4
categories : Head, Arm (containing both arms and hands), Torso, Leg(containing
both legs). And this is the result that we obtained from the ANOVA between gaze
patterns on the AOIs versus the $\mathcal{H}$ and $\mathcal{R}$ conditions :

\textit{\textbf{head}}: the fixations on the head for the $\mathcal{H}$ scene
were observed to more than that for the $\mathcal{R}$ scene (F[1,36] = \ 6.60, p
< .05)

\textit{\textbf{arm}}\ : the fixations on the arms for the $\mathcal{H}$ scene
were also greater than that for the $\mathcal{R}$ scene (F[1,36] = 18.65, p <
.01)

\textit{\textbf{leg}}\hspace{0.18cm} : the fixations on the legs were much lower
for the $\mathcal{H}$ scene as compared to the $\mathcal{R}$ scene (F[1,36] = \
2.89, p < .1)

\textit{\textbf{torso}} : the fixations on the torso was more for the
$\mathcal{H}$ scene than for the $\mathcal{R}$ scene (F[1,36] = \ 3.54, p < .1)

\subsection{H2: Difference in gaze patterns vs ICA}

We got a significant correlation between $\delta_{\mathcal{H},\mathcal{R}}$ and
the ICA. As can be seen in figure 3(a), there is a significant negative
correlation between the two quantities (Pearson Correlation Coefficient = -0.42,
p < .01).

\begin{figure}
    \subfigure[Difference in gaze patterns vs ICA]
    {\includegraphics[width=3.3in]{H2}\label{GazeDifference-vs-ICA}}
    \subfigure[Gaze patterns for high vs low condition]
    {\includegraphics[width=3.3in]{GazeHighLow}\label{GazeHighLow}}
    \subfigure[Difference between ICA and AAP versus High/Low]
    {\includegraphics[width=3.3in]{H4}\label{ICAtoAAPImprovement}}
    \caption{Hypotheses H2, H3, H4}
\end{figure}

@@

This test was done only for $\mathcal{R}$ scenario as the $\mathcal{H}$ case is
by default a source of HC condition, hence, would not make a big impact in
changing the patterns across the LC and HC conditions. Based on ANOVA results,
taking just the 5 AOI groups (head, arms, hands, torso, legs) for the robot in
both LC and HC conditions, the fixations on the head in the HC condition was
found to be significantly higher than that in the LC condition (F[1,36] = 4.55,
p < .05). For all other AOI groups, the fixations across LC and HC were almost
the same. Figure 3(b) shows the distribution of proportion of time spent gazing
on the 5 AOIs for LC and HC conditions.

\subsection{H4: Difference between ICA and AAP versus High/Low}

ANOVA between $\Delta_{ICA,AAP}$ and the category of cognitive task
\ie HC or LC tells us that $\Delta_{ICA,AAP}$ is greater for HC tasks
than that for the LC tasks (F[1,36] = 6.54, p < .05). The results are shown in
figure 3(c).

@@

Based on the results that we obtained, we can now verify our four hypotheses.
For the first hypothesis where we state that the gaze patterns can distinguish
between $\mathcal{H}$ and $\mathcal{R}$ interaction scenarios, we get greater
amount of fixation on the head, arms and torso for the $\mathcal{H}$ scenario as
compared to the $\mathcal{R}$ scenario. This can be explained by the fact that
human is by default perceived as a high cognitive agent compared to a robot.
Hence, the proportion of time spent on looking at the head is more in case of
human videos as compared to robot videos. But the trend is opposite for legs.
This might be explained by the fact that the participants are fascinated by the
joints on the robot's legs \ie the novelty effect. Overall, this
result weakly validates our hypothesis.

In the second hypothesis, where we claim that $\delta_{\mathcal{H},\mathcal{R}}$
should correlate with the participants' ICA, we obtain in our results, a
significant negative correlation between the two quantities. From the negative
correlation, we can understand that if ICA is high, it means that the
\textit{human likeliness ascription} (HLA) is high (which means that there is a
greater tendency to anthropomorphize) which indicates that
$\delta_{\mathcal{H},\mathcal{R}}$ should be low. This supports our hypothesis
and can be explained by the fact that if HLA is high for a participant, then
even the $\mathcal{R}$ videos are quite human-like for such participant.

@@

Finally for the fourth hypothesis where we state that the cognitive priming will
have an effect on $\Delta_{ICA,AAP}$, as seen in the results, $\Delta_{ICA,AAP}$
for participants that watched the HC task is greater than that for the
participants who watched LC task. This proves the fact that HLA was induced by
the videos and in fact, the HC tasks impose a greater HLA on the minds of
participants than the LC tasks. This shows the typical priming effect of the
audio command given in the beginning of the video and highlights the variation
in HLA based on the interaction scenario (LC versus HC) thereby supporting our
hypothesis.

@@

In our experiment, we created two kinds of scenarios each for $\mathcal{H}$ and
$\mathcal{R}$ interaction and just by changing the audio commands (priming
effect), we replicated these videos to create a HC and a LC scene. We recorded
the gaze patterns of the 40 participants who were made to watch these videos and
also the participants were asked to fill two questionnaires before and after the
experiment. These data were analyzed and compared to our four hypotheses. We
hypothesized that one who anthropomorphizes more would have a similar reaction
to $\mathcal{H}$ and $\mathcal{R}$ conditions, and also that in the HC case, a
participant's fixations would be more on the head of the actor as compared to
that in the LC case. We also hypothesized that the HC scene would induce more
anthropomorphic attitude than the LC scene. We found that the results were
successful and supported our hypotheses. We also had another scenario where the
robot/human was asked to move/dance, but this scenario had only one object
(\ie the actor) showing movements, and hence participants would focus
more on seeing the movements leaving behind the cognition aspect, which made it
difficult to differentiate between the LC and HC cases and, therefore, we
discarded this scenario from our analysis.

>>>>

\newcommand{\anti}{{$\mathcal{A}_0$ }}
\newcommand{\antf}{{$\mathcal{A}_1$ }}
\newcommand{\deltaant}{{ $\Delta_{\mathcal{A}_0,\mathcal{A}_1}$ }}

@@

Anthropomorphism is seen as a special kind of social (human-like) engagement
with robots. We made an attempt to analyze anthropomorphism in a
\textit{human-robot} interaction by utilizing the gaze patterns of the
participants (who watched this interaction). These gaze patterns were compared
to the gaze patterns for a similar \textit{human-human} interaction setting. The
``human'' part of the human-robot and human-human interactions mentioned above
is only in the form of an audio command and not physically present in the scene.
Hence, we represent the interactions with robot($\mathcal{R}$) and human($\mathcal{H}$) in
this report for the human-robot and human-human settings respectively.

There were four hypotheses made in this experiment\fxwarning{need to change order of hypotheses(as Kshitij suggested) but the flow breaks by placing H4 first, H1 last}. We hypothesized
(\textbf{H1}) that the gaze patterns can distinguish between human and
robot interaction scenarios. Further, this gaze pattern difference can
be denoted as the distribution of gaze on areas of interest in the scene.
Secondly, we hypothesized (\textbf{H2}) that the difference in gaze patterns
between human and robot conditions
($\delta_{\mathcal{H},\mathcal{R}}$) correlate with the participants'
\textit{initial tendency to anthropomorphize} (\anti), where \anti was measured
as the sum of the ratings (responses) given by the participants to the questions
of the pre-questionnaire. This means that for participants whose \anti is low, the
gaze patterns should be significantly different for the robot videos
compared to the human videos.

We also hypothesized (\textbf{H3}) that the gaze patterns can distinguish
between high-cognitive and low-cognitive tasks. Finally, we hypothesized
(\textbf{H4}) that the cognitive priming will have an effect on the difference
between \anti and \textit{final tendency to anthropomorphize} (\antf) \ie
\deltaant (where \antf is measured for the post-questionnaire in a
similar way as the \anti).

\fxwarning{This whole para already being discussed under Experimental Design. Can remove this para}We used stationary eye tracking technique for tracking the gaze patterns and
``Nao", a robot manufactured by Aldebaran Robotics was used in this
experiment. The
interactions were recorded as videos and were then shown to the participants.
The scenarios that were covered in the videos were aimed at eliciting the
human-like or high-cognitive (HC) feelings for the robot in one setting and
robot-like or low-cognitive (LC) feelings in the other setting. We tried to keep our distribution of
participants uniform across all variations of the scenarios to avoid any biases
to our results. The change in the feelings\fxwarning{can we have a more specific word than 'feeling'?} of participants were recorded in the
form of response to two questionnaires before and after the experiment. The
difference in the response of the two questionnaires was used to measure the
impact the videos had on the participants.

\fxwarning{This para is here just to justify why 3rd scenario isn't used. Else the contents already being discussed in sections 3.1, 3.2}As mentioned earlier, the human element in the robot interaction was in
the form of a command given by the human to the
robot. This command (\eg ``pick up the brown toy") was used to prime
the context thereby classifying the scenario as LC or HC. Initially we had three
different scenarios where the robot/human was asked:

@@

\fxwarning{Is Introduction the best place for justification for not using 3rd scenario?}Differing from first two scenarios, the third scenario had only one object in
the video \ie~the actor (human or robot). In the first two scenarios, a
participant could make gaze transitions, say, between the robot and the toys for
the first scene. In contrast, in the third scene, a participant could only look
at the robot showing its movements. The third scene, hence, was more related to
observing the various body movements and was not helpful in identifying
differences in gaze patterns based on LC and HC scenarios and therefore, we did
not consider it for our study.

\section{Related Work}
\fxwarning{Need to modify (as S\'everin suggested) and curtail it}
In a human-robot interaction, studying anthropomorphism would essentially mean
the assessment of human's tendency to engage in a human like way with robots
(that are not deliberately made to buttress such relationship). In broader
terms, anthropomorphism can be understood as the phenomenon between a human and
a non-human, where the human tends to attribute human characteristics to the
non-human in order to establish a meaningful contact\cite{fink2014dynamics}. But
there have been a plethora of definitions of anthropomorphism not only across
but within disciplines\cite{duffy_anthropomorphism_2002}. Even
within HRI (human robot interaction) and robotics, there has not been a single
unique definition of anthropomorphism, but a variety of them.
Bartneck~\etal\cite{bartneck_measurement_2008} refer to it as \emph{``the
attribution of a human form, human characteristics, or human behavior to
nonhuman things such as robots, computers, and animals."} Contrarily,
Waytz~\etal\cite{Waytz2010} apply a more psychological-cognitive view and
define anthropomorphism as \textit{``a process of inductive inference whereby
    people imbue the real or imagined behavior of other agents with human like
    characteristics, motivations, intentions, or underlying mental states".}

@@

This study is build as an eye-tracking experiment (mainly measuring fixation
times on various body parts) where participants watch short videos of an agent
(either a robot or a human) performing very simple task (picking an object or
pointing toward a sound source), in two different socio-cognitive contexts.
These contexts, created by priming and/or audio cues, are designed to elicit
either a shallow cognitive context (that participant would refer as a
\emph{machine-like} situation) or a deeper cognitive context (refered as a
\emph{human-like} situation).

@@

    \caption{\small The study follows a 2x2 design: the \emph{robot} vs
        \emph{human} condition is within subject, while the \emph{shallow
        cognitive context} vs \emph{deep cognitive context} is between subject.
        Two stimuli (\emph{Picking} task, {\bf A}, and \emph{Sound} task,
        {\bf B}) were shown to the participants, introduced by brief verbal
        commands, reproduced in the table. While visually identical (see
        screenshots on figure~\ref{fig:stimuli}), the stimuli were introduced
        with different commands in the two conditions \emph{shallow} and
        \emph{deep cognitive
        context}.}

@@

@@

\subsection{Questionnaires}

Before starting the experiment, the participants were asked to fill a
questionnaire which had 49 questions. The responses to the questions were scaled
in the 5-point Likert scale, numerically ranging from -2 to 2. The questionnaire
had ten questions from the 10 item big-five personality questionnaire. And then
there were questions taken from Godspeed questionnaire and other
questionnaires. In this report, we refer to this questionnaire as the
pre-questionnaire \ie before the experiment, and it typically took 5 minutes for
participants to fill it.

A second questionnaire was administered at the end of the experiment, that was
almost identical to the pre-questionnaire.  This questionnaire typically took 3
to 4 minutes to fill and we refer to this as the post-questionnaire.

The difference (noted \deltaant, computation detailed below) observed for
each participant between the pre- and post-questionnaires form the dependent
variable of our experiment. It reflects the impact of the video stimuli on the
anthropomorphic perception that they have of robots \emph{in general}: the
Godspeed questions used in the questionnaires are not specific to the Nao robot,
and assess in a broader way how humans perceive robots.

\section{Experiment}

@@

The participants were recruited amongst students of our university. To avoid students
with a higher familiarity with robots and artificial intelligent systems,
Computer Science and Electronics curriculum were excluded. This was \textit{a
posteriori} comforted as per the questionnaire responses: no
participants\fxwarning{to be checked : actually 5 out of 40 reported to be familiar(they marked +1 or +2 in questionnaire)}
reported itself as being familiar with robots and only a few\fxwarning{how
many? ( = 8 out of 40 )} out of 40 had ever owned a robot.

@@

\subsubsection{Pre-questionnaire and familiarization}

\fxwarning{Was it first the pre-questionnaire or the familiarization?}
Before the experiment, participants were made to read, understand and sign a
standard consent form. Participants were then asked to fill the 49 questions of
the pre-questionnaire, without time constraint\fxwarning{right?}.

After the pre questionnaire, we invited the participants to an initial
free interaction with a \textbf{powered-off} Nao robot (we did not constraint
the time, and participants played between 2 and 3 minutes ith the robot).

The purpose of this pre-interaction was to get the participants acquainted with the
robot shape and kind of motions it could possibly perform, and therefore
mitigate the (visual) novelty effect (so that they do not get surprised seeing
a robot for the first time in the videos).

@@

After filling the pre-questionnaire, we conducted a brief eye-tracker
calibration procedure, and the participants' gaze was recorded while they
watched the \emph{robot} and \emph{human} interaction videos.

@@

Finally, the participants were asked to fill the post-questionnaire.

Before leaving, each of the participants were given a reward equivalent to CHF
10.

@@

\subsubsection{Questionnaires processing}

\fxnote{TDB}

Questionnaires were coded and two values, the \emph{initial tendency to
anthropomorphize} \anti and the \emph{final tendency to anthropomorphize} \antf
were computed, respectively from the pre- and post-questionnaires.

These values were computed by a direct sum of the rating provided by the
participants for the Godspeed's questions in the category
\emph{Anthropomorphism} and \emph{\fxwarning{?}...}. These ten questions were
rated between -2 and 2, hence \anti and \antf vary between -20 and 20.

The other questions (including the Big-Five personality test) were not used for
this study.

@@

Based on the experiments conducted on 40 participants in the $\mathcal{H}$ and
robot interactions across LC and HC conditions, we have the following
results. (The detailed statistics and code used for obtaining the results are
available here : \url{https://github.com/chili-epfl/anthropomorphism-eyetracking})

@@

Among the 10 AOIs, we grouped the AOIs corresponding to the actor into 4
categories : Head, Arm (containing both arms and hands), Torso, Leg(containing
both legs). And this is the result that we obtained from the ANOVA between gaze
patterns on the AOIs versus the human and robot videos :

\textit{\textbf{head}}: the fixations on the head for the human video
were observed to more than that for the robot video (F[1,36] = \ 6.60, p
< .05)

\textit{\textbf{arm}}\ : the fixations on the arms for the $\mathcal{H}$ video
were also greater than that for the robot video (F[1,36] = 18.65, p <
.01)

\textit{\textbf{leg}}\hspace{0.18cm} : the fixations on the legs were much lower
for the human video as compared to the robot video (F[1,36] = \
2.89, p < .1)

\textit{\textbf{torso}} : the fixations on the torso was more for the
human video than for the robot video (F[1,36] = \ 3.54, p < .1)

\subsection{H2: Difference in gaze patterns vs \anti}

We got a significant correlation between $\delta_{\mathcal{H},\mathcal{R}}$ and
the \anti. As can be seen in figure 3(a), there is a significant negative
correlation between the two quantities (Pearson Correlation Coefficient = -0.42,
p < .01).

\begin{figure}
    \subfigure[Difference in gaze patterns vs \anti]
    {\includegraphics[width=3.3in]{H2}\label{GazeDifference-vs-ICA}}
    \subfigure[Gaze patterns for high vs low condition]
    {\includegraphics[width=3.3in]{GazeHighLow}\label{GazeHighLow}}
    \subfigure[Difference between \anti and \antf versus High/Low]
    {\includegraphics[width=3.3in]{H4}\label{ICAtoAAPImprovement}}
    \caption{Hypotheses H2, H3, H4}
\end{figure}

@@

This test was done only for robot scenario as the human case is
by default a source of HC condition, hence, would not make a big impact in
changing the patterns across the LC and HC conditions. Based on ANOVA results,
taking just the 5 AOI groups (head, arms, hands, torso, legs) for the robot in
both LC and HC conditions, the fixations on the head in the HC condition was
found to be significantly higher than that in the LC condition (F[1,36] = 4.55,
p < .05). For all other AOI groups, the fixations across LC and HC were almost
the same. Figure 3(b) shows the distribution of proportion of time spent gazing
on the 5 AOIs for LC and HC conditions.

\subsection{H4: Difference between \anti and \antf versus High/Low}

ANOVA between \deltaant and the category of cognitive task
\ie HC or LC tells us that \deltaant is greater for HC tasks
than that for the LC tasks (F[1,36] = 6.54, p < .05). The results are shown in
figure 3(c).

@@

Based on the results that we obtained, we can now verify our four hypotheses.
For the first hypothesis where we state that the gaze patterns can distinguish
between human and robot interaction scenarios, we get greater
amount of fixation on the head, arms and torso for the human scenario as
compared to the robot scenario. This can be explained by the fact that
human is by default perceived as a high cognitive agent compared to a robot.
Hence, the proportion of time spent on looking at the head is more in case of
human videos as compared to robot videos. But the trend is opposite for legs.
This might be explained by the fact that the participants are fascinated by the
joints on the robot's legs \ie the novelty effect. Overall, this
result weakly validates our hypothesis.

In the second hypothesis, where we claim that $\delta_{\mathcal{H},\mathcal{R}}$
should correlate with the participants' \anti, we obtain in our results, a
significant negative correlation between the two quantities. From the negative
correlation, we can understand that if \anti is high, it means that the
\textit{human likeliness ascription} (HLA) is high (which means that there is a
greater tendency to anthropomorphize) which indicates that
$\delta_{\mathcal{H},\mathcal{R}}$ should be low. This supports our hypothesis
and can be explained by the fact that if HLA is high for a participant, then
even the robot videos are quite human-like for such participant.

@@

Finally for the fourth hypothesis where we state that the cognitive priming will
have an effect on \deltaant, as seen in the results, \deltaant
for participants that watched the HC task is greater than that for the
participants who watched LC task. This proves the fact that HLA was induced by
the videos and in fact, the HC tasks impose a greater HLA on the minds of
participants than the LC tasks. This shows the typical priming effect of the
audio command given in the beginning of the video and highlights the variation
in HLA based on the interaction scenario (LC versus HC) thereby supporting our
hypothesis.

@@

In our experiment, we created two kinds of scenarios each for human and
robot interaction and just by changing the audio commands (priming
effect), we replicated these videos to create a HC and a LC scene. We recorded
the gaze patterns of the 40 participants who were made to watch these videos and
also the participants were asked to fill two questionnaires before and after the
experiment. These data were analyzed and compared to our four hypotheses. We
hypothesized that one who anthropomorphizes more would have a similar reaction
to human and robot conditions, and also that in the HC case, a
participant's fixations would be more on the head of the actor as compared to
that in the LC case. We also hypothesized that the HC scene would induce more
anthropomorphic attitude than the LC scene. We found that the results were
successful and supported our hypotheses. We also had another scenario where the
robot/human was asked to move/dance, but this scenario had only one object
(\ie the actor) showing movements, and hence participants would focus
more on seeing the movements leaving behind the cognition aspect, which made it
difficult to differentiate between the LC and HC cases and, therefore, we
discarded this scenario from our analysis.
